### 2018-11-28 chapters/3-results.tex
restructuring

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Table~\ref{tab:auc_imagetype} contains the
results for models within each image type using all or top 1\% of the features.

@@

\subsection{All features of individual image type}

@@

\subsection{Selected features of individual image type}

@@

\subsection{All features of combined image types}

@@

\subsection{Selected features of combined image types}

>>>>

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Table~\ref{tab:auc_imagetype} contains the
results for models within each image type using all or top 1\% of the features.
The results are AUC values with confidence intervals included.

@@

\subsubsection{All features within individual image types}

@@

\subsubsection{Selected features within individual image types}

@@

\subsubsection{All features of combined image types}

@@

\subsubsection{Selected features of combined image types}
